Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edit
change to the model component plot

The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, \mathrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time. 
% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The components of the model are shown in Figure~\ref{fig:Modelcomponents}
\begin{figure}[!t]
\centering
\includegraphics[scale=.8]{./Graph/ModelComponents.pdf}
\caption{ {\bf The IDE neural field model components}. (\textbf{A}) The Mexican hat (red) and Wizard hat (blue) connectivity kernels. (\textbf{B}) First order (red) and second order (blue) synaptic kernels. (\textbf{C}) A representative of the activation function.}
\label{fig:Modelcomponents}
\end{figure}

>>>>

The stochastic IDE form of the Amari neural field formulation~\cite{Amari1977} is given by (see~\cite{Freestone2011} for a full derivation)
\begin{equation}\label{eq:DiscreteTimeModel}
	v_{t+1}\left(\mathbf{r}\right) = 
	\xi v_t\left(\mathbf{r}\right) + 
	T_s \int_\Omega { 
	    w\left(\mathbf{r},\mathbf{r'}\right)
	    f\left(v_t\left(\mathbf{r}'\right)\right) 
	\, \mathrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
\end{equation}
where in this first-order (in time) form of the model the membrane dynamics are included through the parameter $\xi=1-T_s/\tau$, where $\tau$ is the membrane time constant and $T_s$ is the sampling time. 
% The connectivity strength between neural populations at a distance $\mid\mathbf{r}-\mathbf{r'}\mid$ is described by the connectivity kernel $w\left(\mathbf{r}-\mathbf{r}'\right)$. The connectivity kernel is taken as a ``Mexican hat'' function, which describes local excitation and lateral inhibition \cite{Amari1977,Atay2005}. The components of the model are shown in Figure~\ref{fig:Modelcomponents}
\begin{figure}[!t]
\centering
\includegraphics[scale=1]{./Graph/ModelComponents.pdf}
\caption{ {\bf The IDE neural field model components}. (\textbf{A}) The Mexican hat (dotted line) and Wizard hat (solid line) connectivity kernels. (\textbf{B}) First order (dotted line) and second order (solid line) synaptic kernels. (\textbf{C}) A representative of the activation function.}
\label{fig:Modelcomponents}
\end{figure}
